An umbrella review of the benefits and risks associated with youths' interactions with electronic screens

### 2023-08-02 reports/manuscript.tex
Rerun pipeline

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{\newline\indent Word count: 5299}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\abstract{%
The influence of electronic screens on children and adolescents' health and education is not well understood.
In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from 102 meta-analyses (2,451 primary studies; 1,937,501 participants) on screen time and any outcome for youths.
Of these, 43 effects from 32 met our criteria for statistical certainty.
Some types of screen use, such as social media, were consistently correlated with risks (e.g., depression, \emph{r} = 0.12, 95\% confidence interval {[}CI{]} 0.05 to 0.19, \emph{p} = \textless0.001, \emph{k} = 12, \emph{N} = 93,740) while others, such as educational screen use, showed associations with benefits (e.g., motivation for learning, \emph{r} = 0.16, 95\% CI 0.02 to 0.31, \emph{p} = 0.029, \emph{k} = 10, \emph{N} = 1,183).
Some types of screen use have complex associations with outcomes.
For example, television viewing showed harmful correlations with learning (\emph{r} = -0.10, 95\% CI -0.15 to -0.04, \emph{p} = \textless0.001, \emph{k} = 18, \emph{N} = 62,135).
However, when parents watched with their children, general screen use was associated with greater literacy (\emph{r} = 0.15, 95\% CI 0.02 to 0.28, \emph{p} = 0.028, \emph{k} = 12, \emph{N} = 6,083).
These findings suggest that caregivers need to carefully weigh the pros and cons of each specific activity for potential harms and benefits.
}

@@

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{\newline\indent Word count: 5300}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\abstract{%
The influence of electronic screens on children and adolescents' health and education is not well understood.
In this prospectively registered umbrella review (PROSPERO; CRD42017076051), we harmonised effects from 102 meta-analyses (2,451 primary studies; 1,937,501 participants) on screen time and outcomes.
43 effects from 32 meta-analyses met our criteria for statistical certainty.
Meta-analyses of associations between screen use and outcomes showed small-to-moderate effects (range: \emph{r} = -0.14-0.33).
In education, results were mixed; for example, screen use was negatively associated with literacy (\emph{r} = -0.14, 95\% confidence interval {[}CI{]} -0.20 to -0.09, \emph{p} = \textless0.001, \emph{k} = 38, \emph{N} = 18,318), but this effect was positive when parents watched with their children (\emph{r} = 0.15, 95\% CI 0.02 to 0.28, \emph{p} = 0.028, \emph{k} = 12, \emph{N} = 6,083).
In health, we found evidence for several small negative associations; for example, social media was associated with depression (\emph{r} = 0.12, 95\% CI 0.05 to 0.19, \emph{p} = \textless0.001, \emph{k} = 12, \emph{N} = 93,740).
Limitations include a limited number of studies for each outcome, medium-to-high risk of bias in 95/102 included meta-analyses and high heterogeneity (17/22 in education and 20/21 in health with \(I^2 > 50\%\))
We recommend that caregivers carefully weigh the potential harms and benefits of specific types of screen use.
}

@@

\begin{ThreePartTable}
\begin{TableNotes}
\item \textit{Note: } 
\item Items are from the National Health, Lung and Blood Institute's Quality Assessment of Systematic Reviews and Meta-Analyses tool. Note that we excluded the first item of the tool. U = Unclear; L = Low; H = High
\item[1] Eligibility criteria predefined and specified
\item[2] Literature search strategy comprehensive and systematic
\item[3] Dual independent screening and review
\item[4] Dual independent quality assessment
\item[5] Included studies listed with important characteristics and results of each
\item[6] Publication bias assessed
\item[7] Heterogeneity assessed
\end{TableNotes}
\begin{longtable}[t]{ll>{\centering\arraybackslash}p{1.25cm}>{\centering\arraybackslash}p{1.25cm}>{\centering\arraybackslash}p{1.25cm}>{\centering\arraybackslash}p{1.25cm}>{\centering\arraybackslash}p{1.25cm}>{\centering\arraybackslash}p{1.25cm}>{\centering\arraybackslash}p{1.25cm}}
\caption{Quality assessment for studies providing unique effects}\\
\toprule
\multicolumn{2}{c}{ } & \multicolumn{7}{c}{Quality Assessment} \\
\cmidrule(l{3pt}r{3pt}){3-9}
First Author & Year & Elig. Crit.\textsuperscript{1} & Lit. Search\textsuperscript{2} & Dual Screen\textsuperscript{3} & Dual Qual.\textsuperscript{4} & Studies Listed\textsuperscript{5} & Pub. Bias\textsuperscript{6} & Hetero.\textsuperscript{7}\\
\midrule
\endfirsthead
\caption[]{Quality assessment for studies providing unique effects \textit{(continued)}}\\
\toprule
First Author & Year & Elig. Crit.\textsuperscript{1} & Lit. Search\textsuperscript{2} & Dual Screen\textsuperscript{3} & Dual Qual.\textsuperscript{4} & Studies Listed\textsuperscript{5} & Pub. Bias\textsuperscript{6} & Hetero.\textsuperscript{7}\\
\midrule
\endhead

\endfoot
\bottomrule
\insertTableNotes
\endlastfoot
Abrami & 2020 & U & U & L & H & L & L & L\\
Adelantado-Renau & 2019 & L & L & L & L & L & L & L\\
Andrade & 2019 & U & L & L & U & L & H & L\\
Arztmann & 2022 & U & H & H & H & H & L & L\\
Aspiranti & 2020 & U & L & L & H & L & H & L\\
\addlinespace
Bartel & 2015 & L & L & U & U & L & U & U\\
Beck Silva & 2022 & L & L & L & L & L & H & L\\
Benavides-Varela & 2020 & U & H & L & H & L & L & L\\
Blok & 2002 & U & L & H & H & L & H & L\\
Bossen & 2020 & U & L & L & L & L & H & L\\
\addlinespace
Boyland & 2016 & H & L & L & U & L & L & L\\
Byun & 2018 & U & U & U & H & H & H & H\\
Cao & 2020 & U & H & U & H & L & L & L\\
Champion & 2019 & L & L & L & L & L & L & L\\
Chan & 2014 & U & H & H & H & L & L & L\\
\addlinespace
Chauhan & 2017 & U & L & U & H & H & L & L\\
Chen & 2020 & U & H & U & H & H & H & L\\
Cheung & 2012 & U & L & L & H & H & L & L\\
Cheung & 2013 & L & H & H & U & L & L & L\\
Cho & 2018 & U & H & U & H & L & L & L\\
\addlinespace
Claussen & 2022 & U & L & U & H & L & H & L\\
Clinton & 2019 & U & H & U & U & L & L & L\\
Comeras-Chueca & 2021 & L & U & L & U & L & H & L\\
Comeras-Chueca & 2021 & L & L & L & U & L & H & L\\
Coyne & 2018 & L & L & L & H & L & L & L\\
\addlinespace
Cunningham & 2021 & U & L & L & H & L & L & L\\
Cushing & 2010 & U & L & H & H & L & L & L\\
Darling & 2017 & U & L & U & U & L & H & H\\
Eirich & 2022 & U & L & L & L & L & L & L\\
Feng & 2021 & L & L & L & L & L & H & L\\
\addlinespace
Ferguson & 2017 & U & L & L & H & L & L & L\\
Ferguson & 2020 & L & U & L & L & L & L & L\\
Folkvord & 2018 & U & L & L & U & L & H & L\\
Furenes & 2021 & H & H & L & U & L & L & L\\
Gardella & 2017 & U & L & L & U & L & L & L\\
\addlinespace
Garzón & 2019 & U & H & U & H & H & L & L\\
Graham & 2015 & U & L & H & H & L & L & L\\
Hammersley & 2016 & L & L & H & L & L & H & L\\
Hao & 2021 & U & L & L & L & L & H & L\\
Hassan-Saleh & 2019 & U & L & U & U & H & H & L\\
\addlinespace
He & 2021 & L & L & L & L & L & L & L\\
Hernandez-Jimenez & 2019 & U & L & H & L & L & L & L\\
Hurwitz & 2018 & L & L & H & H & L & L & L\\
Ivie & 2020 & U & L & L & L & L & L & L\\
Janssen & 2020 & U & L & L & L & L & U & L\\
\addlinespace
Kates & 2018 & U & H & L & H & H & L & L\\
Kim & 2021 & U & L & U & L & L & L & L\\
Kroesbergen & 2003 & U & L & U & H & L & H & L\\
Kucukalkan & 2019 & U & L & U & U & H & L & L\\
Li & 2010 & U & L & L & U & L & H & L\\
\addlinespace
Li & 2022 & L & H & L & L & L & H & L\\
Li & 2022 & U & H & L & H & L & L & L\\
Liao & 2008 & L & H & H & L & H & H & H\\
Liao & 2014 & U & L & H & L & L & L & L\\
Liu & 2019 & U & L & U & H & L & L & L\\
\addlinespace
Liu & 2022 & U & H & U & H & H & L & L\\
Lu & 2021 & U & L & U & L & L & L & L\\
Madigan & 2020 & U & L & L & U & L & L & L\\
Major & 2021 & U & L & L & H & L & L & L\\
Mallawaarachchi & 2022 & L & L & L & L & L & L & L\\
\addlinespace
Mares & 2005 & U & L & H & H & L & H & H\\
Mares & 2013 & U & H & H & H & L & H & L\\
Marker & 2022 & U & L & H & L & L & L & L\\
Marshall & 2004 & U & L & H & H & H & H & L\\
Martins & 2019 & U & L & U & H & L & L & L\\
\addlinespace
Martins & 2022 & L & L & L & L & L & H & L\\
Mazeas & 2022 & L & L & L & L & L & L & L\\
McArthur & 2012 & L & L & L & L & L & L & L\\
McArthur & 2018 & L & L & L & L & L & L & L\\
Mei & 2018 & U & H & U & L & L & H & L\\
\addlinespace
Merchant & 2014 & U & L & H & H & H & H & L\\
Neitzel & 2022 & U & L & H & H & L & H & H\\
Oldrati & 2020 & U & L & U & H & L & L & L\\
Paik & 1994 & U & H & U & H & H & L & H\\
Pearce & 2016 & U & L & H & H & H & L & L\\
\addlinespace
Peng & 2011 & U & L & U & U & L & H & L\\
Powers & 2013 & U & L & U & H & L & L & L\\
Prescott & 2018 & U & L & U & H & L & L & L\\
Reynard & 2022 & H & L & L & L & L & L & L\\
Rodriguez-Rocha & 2019 & U & L & L & L & L & L & L\\
\addlinespace
Sadeghirad & 2016 & H & L & L & L & L & L & L\\
Scherer & 2020 & U & H & U & H & L & L & L\\
Schroeder & 2013 & L & L & U & H & L & L & L\\
Scionti & 2019 & L & L & L & H & L & L & L\\
Shin & 2019 & U & L & L & L & L & H & L\\
\addlinespace
Shin & 2022 & L & H & L & L & L & L & L\\
Slavin & 2014 & U & H & H & H & L & H & H\\
Strouse & 2021 & U & L & U & H & H & L & L\\
Takacs & 2014 & H & L & U & H & L & L & L\\
Takacs & 2019 & L & L & U & H & L & L & L\\
\addlinespace
Tekedere & 2016 & U & H & U & U & L & L & L\\
Tokac & 2019 & U & H & L & H & L & L & L\\
Vahedi & 2018 & L & L & U & U & L & L & L\\
van Ekris & 2016 & U & L & L & L & L & H & L\\
Vannucci & 2020 & U & L & U & H & L & L & L\\
\addlinespace
Williams & 1982 & U & U & H & U & L & H & H\\
Wouters & 2013 & U & H & U & H & L & L & L\\
Xie & 2018 & U & L & L & H & L & L & L\\
Yin & 2019 & U & H & U & H & L & L & L\\
Zhou & 2020 & U & L & U & H & L & L & L\\
\addlinespace
Zucker & 2009 & L & L & U & H & L & H & L\\*
\end{longtable}
\end{ThreePartTable}
